---
title: "Scalable Text Mining for Large Escanning Datsets"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

##Synopsis: 

##Harvested the original data of approximately 5500 e-scanned articles from IBM Watson to the E-scanning database (called Mongo), and saved in disk drive. Sandard text processing and cleaning ("the", "and", "ing", ";", ":" etc.,) simplified the ensuing  three types text analyses using R text mining  packages.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=F}
library("tm")#CallEd the 2 packages to process the datA
library ("SnowballC")  
```

```{r include=F}
cname <- file.path("C:", "texts")# Showed R where the text is stored for analysis
docs <- Corpus(DirSource(cname))# Create a Corpus for further analysis
```


## DATA PROCESSING

```{r include=T}
docs <- tm_map(docs, removePunctuation) 
docs <- tm_map(docs, removeNumbers)
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, stripWhitespace) 
docs <- tm_map(docs, stemDocument) #Removing common word endings (e.g., "ing", "es", "s") 
dtm <- DocumentTermMatrix(docs) #create matrices that help the futher analysis
dtmss <- removeSparseTerms(dtm, 0.06) # This makes a matrix that is 6% empty space, maximum. 
```


## ANALYSIS


## 1. Most Frequent Words 

```{r include=T}
#org by freq
freq <- colSums(as.matrix(dtm))  
ord <- order(freq) 
freq[tail(ord, n=10)] 
```


## 2. Word Cloud 

```{r include=T}
library("wordcloud")
#100 most frequently used words.
set.seed(142)   
wordcloud(names(freq), freq, max.words=20, colors=brewer.pal(25, "Dark2"))
```


## 3. Clustering

## Creating a cluster of n (here n=4) using Clara for Clustering Large Applications.  Compared to other partitioning methods such as pam, Clara can deal with much larger datasets. Clara is fully described in chapter 3 of Kaufman and Rousseeuw (1990) ``Finding Groups in Data''

```{r include=T}
library("cluster")
d <- dist(t(dtmss), method = "euclidian")
clara(as.matrix(d), 4, samples = 20, sampsize = 25)

```
